---
title: "Focus of Research"
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Generally

| Analyses of patterns   | Atlantic, Gulf and Carribean Habitats |
|------------------------|---------------------------------------|
| Presence-absence       | Seagrass                              |
| density-biomass        | Marsh                                 |
| growth-mortality       | Mangrove                              |
| production             | Coral                                 |
| abundance-distribution | Marine, general                       |
| genetics               | Coastal, general                      |
| immigration-emigration |                                       |

This is a basic page with no table of contents. You specify this type of page with

    output:
      distill::distill_article:
        self_contained: false

## R code

Because this uses RMarkdown. You can have R code.

```{r}
render(./StaffPostCards/index.Rmd)
```

```{r echo=FALSE}
plot(1,1)
```
